The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-03-31 VegOzone.tex
Updated text. Included new plots.

\begin{figure*}[t]
  \includegraphics[width=12cm]{data_svanvik_2018_2019}
  \caption{Observational data from atmospheric monitoring at Svanhovd in 2018/19. The hatched areas indicate missing ozone monitoring data. (a) Ozone; (b) temperature; (c) daily accumulated precipitation.}
  \label{fig:data_svanvik_2018_2019}
\end{figure*}

@@

\subsubsection{Surface ozone observations}
\label{subsubsec:ebas}
All surface ozone observations used in this study are available from NILU EBAS database. Data for the 2018/19 growing season at Svanhovd have not yet been made available \emph{alternative: shall be made available at a later point}. In Table~\ref{tab:ebas_obs}, we give an overview over the exact locations and time range of operational data taking.

@@

@@

>>>>

\begin{figure*}[t]
  \includegraphics[width=12cm]{data_svanvik_2018_2019}
  \caption{Observational data from atmospheric monitoring at Svanhovd in 2018/19. The hatched areas indicate missing ozone monitoring data. (a) Ozone; (b) temperature; (c) daily accumulated precipitation; (d) hourly global radiation.}
  \label{fig:data_svanvik_2018_2019}
\end{figure*}

@@

\subsubsection{Surface ozone observations}
\label{subsubsec:ebas}
All surface ozone observations used in this study are available from the EBAS database. In Table~\ref{tab:ebas_obs}, we give an overview over the exact locations and time range of operational data taking.

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{global_rad_signific}
  \caption{Global radiation at Svanvik. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. (a) 2018; (b) 2019. Negative deviations from climatology are shown as negative percentaged. The annual positive/negative deviation are indicated in the respective corners (right upper/ right lower).}
  \label{fig:global_rad_signific}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{global_rad_clim}
  \caption{Observed global radition at Svanvik. The grey lines indicate the $1\,\sigma$ level deducted from the climatology. (a) Climatology (hourly maxima, mean, and minima); deviation from climatology (b) 2018; (c) 2019.}
  \label{fig:global_rad_clim}
\end{figure}
